\chapter*{Acknowledgements}

Firstly, I would like to thank my supervisor Ulrik Egede. I would like to thank you for all the support, time and article corrections that you have invested in me. You have given me the opportunity to grow as physicist as well as you taught me to appreciate solving problems differently. You have given me the freedom to follow many different activities such as conferences, hardware, as well as detector maintance all leading to meeting many great people that I am happy to call my friends.

To you Patrick Owen, I owe a big thank you for showing me all the support throughout my entire analysis. Without your great insight and motivation that you have kept even when you changed institute, it would have been completely different journey. 

I would also like to express special thanks to Mike McCainn, whose patience knows no limits, but apparently LHC's is 15 minutes. I learnt how handle many power-cycling buttons as well as croquet. Here I would also like to extend my gratitute to many of the RICH collaborators such as Antonis, Silvia, Roberta whom I have met while working with the upgrade.

And ofcourse all the Imperial crew: Dave, Andrei, Mitesh, Paula, Eluned, Will, Fede, Sophie, Matt, Felix and Malte, who all have their part in this work.

None of this would be possible without the STFC, the finacial body on behalf of British government, who financially supported my PhD and the LHCb collaboration as a whole.

Lastly but most importantly, I would like to thank my family. I have never heard from you that something cannot be done. You have taught me to be curious, to be independent, to be strong. We have sacrified the most precious commodity, time spent together, in order for me to follow my interests. And below is just one example it was all worth it.  


%I would like to thank Mitesh for his continued support throughout my PhD. I am well aware that the amount of time he gives to his students goes above and beyond the norm and as such count myself lucky to have had him as a supervisor\footnote{He is also now one of a select group of people who can understand me even when I break out into full-speaking-speed (or at least I think he can), which in itself deserves some kind of recognition}. A big thank you for everything.
%
%I am also indebted to Patrick Owen for the invaluable input he made to both analyses presented in this thesis. Thank you. I received a huge amount of support and feedback from all members of the Imperial College LHCb group, particularly from Ulrik Egede and Paula \'Alvarez Cartelle. In addition, from  Sam Hall and William Sutcliffe, who were great company both in and out of work.
%
%I would also like to thank the STFC funding body, who financed my PhD and the LHCb collaboration as a whole, who made the work in this thesis possible.
%
%To my Genevan friends, who made a foreign city feel like home. \` A C\'eline, pour toutes nos adventures sportives, a Lorena, por todas las noches de juerga, and to Hannah, who I was lucky enough to have as continued company throughout the last eight years.  A big thank you goes to Ellie, because nothing says friendship like letting me loose on your home for a month. 
%
%To Mark, who can take much credit for the retention of most of my sanity over the last year.
%
%And finally to my family, for consistently being fabulous, throughout my PhD and always. %(and in the latter case who I promise to see more of now I've handed in). 





















